### 2022-06-07 src/text/2-package-subsections/maps.tex
minor changes to maps

\subsection{gammapy.maps}
\label{ssec:gammapy-maps}
\todo{Laura Olivera-Nieto}
The \verb|gammapy.maps| sub-package provides classes for representing data structures associated with a set of coordinates or a region on a sphere. In addition it allows to handle an arbitrary number of non-spatial data dimensions, such as time or energy. It is organized around three types of structures: geometries, sky-maps and map axes, which inherit from the base classes Geom, Map and MapAxis respectively.

The geometry defines the pixelization scheme and map boundaries. It also provides methods to transform between sky and pixel coordinates. Maps consist of a geometry instance together with a data array containing the corresponding map values. Map axes contain a sequence of ordered values which define bins on a given dimension, spatial or not. Map axes can have physical units attached to them, as well as non-linear step sizes.

The sub-package provides a uniform API for the FITS World Coordinate System (WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and region-based data structures.

@@

	\caption{Using gammapy.maps to create a WCS, a HPX and a region map. Note the uniform API for map creation.}
	\label{ig*:minted:gp_maps}
\end{figure}

>>>>

\subsection{gammapy.maps}
\label{ssec:gammapy-maps}
\todo{Laura Olivera-Nieto}
The \verb|gammapy.maps| sub-package provides classes that represent data
structures associated with a set of coordinates or a region on a sphere. In
addition it allows to handle an arbitrary number of non-spatial data
dimensions, such as time or energy. It is organized around three types of
structures: geometries, sky-maps and map axes, which inherit from the base
classes Geom, Map and MapAxis respectively.

The geometry object defines the pixelization scheme and map boundaries. It also
provides methods to transform between sky and pixel coordinates. Maps consist
of a geometry instance together with a data array containing the corresponding
map values. Map axes contain a sequence of ordered values which define bins on
a given dimension, spatial or not. Map axes can have physical units attached to
them, as well as non-linear step sizes.

The sub-package provides a uniform API for the FITS World Coordinate System
(WCS)~\citep{Calabretta2002}, the HEALPix pixelization~\citep{Gorski2005} and
region-based data structure (see Figure~\cite{ig*:minted:gp_maps}).

@@

	\caption{Using gammapy.maps to create a WCS, a HEALPix and a region
		map. Note the uniform API for map creation.} \label{ig*:minted:gp_maps}
\end{figure}
